\papertitle

### 2012-10-13 manuscript.tex
Updated quaternion section for clarity.

Our implementation of quaternion-based control is similar to Knoebe's~\cite{knoebe:quatcontrol}:
Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose (Eq.~\ref{eq:quat_error}). 
\begin{equation}
\label{eq:quat_error}
q_e = q'\otimes q_r
\end{equation}
We then convert this error quaternion to an angle axis, and use this 
representation as input to the PID controller 
(Eqs.~\ref{eq:quat_angle} and~\ref{eq:quat_linearize}). 
\begin{equation}
\label{eq:quat_angle}
\alpha = 2\arccos(q_{e,w})
\end{equation}
\begin{equation}
\label{eq:quat_linearize}
Q_e = \alpha*q_e/\sin(\alpha /2)
\end{equation}

>>>>

Our implementation of quaternion-based control is similar to Knoebe's~\cite{knoebe:quatcontrol}:
Given a reference pose represented in quaternion form $q_r$, we define the error as the rotation $q_e$ 
required to reach the reference pose from the estimated pose $q$ (Eq.~\ref{eq:quat_error}). 
\begin{align}
\label{eq:quat_error}
q_e &= q^{\prime}\cdot q_r \\
		&= q_{e,w} + q_{e,x}\hat{i} + q_{e,y}\hat{j} + q_{e,z}\hat{k} \notag 
\end{align}
We then convert this error quaternion to an angle axis representation and use this 
as input to the PID controller (Eqs.~\ref{eq:quat_linearize} and~\ref{eq:quat_angle}).
These calculations are performed onboard with trigonometric lookup tables for speed.
\begin{align}
\label{eq:quat_linearize}
Q_e &= \alpha\cdot q_e/\sin(\alpha /2) \\
		&= \alpha_{x}\hat{i} + \alpha_{y}\hat{j} + \alpha_{z}\hat{k} \notag
\end{align}
\begin{equation}
\label{eq:quat_angle}
\alpha = 2\arccos(q_{e,w})
\end{equation}
